Crystal as a Thermodynamic Computer

### 2024-09-04 paper/main.tex
update

\title{Surface programmable materials}

@@

\begin{abstract}
\end{abstract}

>>>>

\title{Crystal as a Thermodynamic Computer}

@@

\begin{abstract}
    Thermodynamic computers are believed to be more energy efficient than conventional computers, however, a practical implementation of a thermodynamic computer is still challenging. In this paper, we propose a thermodynamics driven computer that enables use to perform computation by editing its surface.
    The crystalline structure is based on a universal elementary cellular automata, and is translational invariant in all spacial dimensions. The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
\end{abstract}
